---
title: "Decision Space Report"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: pdf_document
params:
  choiceA: "Choice A"
  choiceB: "Choice B"
  mean_A: 0
  mean_B: 0
  mean_D: 0
  width_D: 0
  p_AgtB: 0
  p_BgtA: 0
  p_within5: 0
  threshold_stats: NULL
  intervals_tbl: NULL
  plot_dist_path: ""
  plot_diff_path: ""
  included_aspects: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
library(kableExtra)
```

## Executive Summary

This report compares **`r params$choiceA`** and **`r params$choiceB`** across multiple decision aspects using Monte Carlo simulation (5,000 iterations).

**Included Aspects:** `r params$included_aspects`

### Key Findings

- **Mean Scores:** `r params$choiceA` = `r sprintf("%.3f", params$mean_A)`, `r params$choiceB` = `r sprintf("%.3f", params$mean_B)`
- **Mean Difference:** `r sprintf("%.3f", params$mean_D)` (90% interval width: `r sprintf("%.3f", params$width_D)`)
- **P(`r params$choiceA` > `r params$choiceB`):** `r sprintf("%.1f%%", params$p_AgtB * 100)`
- **P(`r params$choiceB` > `r params$choiceA`):** `r sprintf("%.1f%%", params$p_BgtA * 100)`
- **P(within 5%):** `r sprintf("%.1f%%", params$p_within5 * 100)` (ratio between 0.95 and 1.05)

\newpage

## Score Distributions

```{r plot-distributions, fig.height=4}
knitr::include_graphics(params$plot_dist_path)
```

## Difference Distribution

```{r plot-difference, fig.height=4}
knitr::include_graphics(params$plot_diff_path)
```

\newpage

## Threshold Probabilities

The following table shows the probability that one choice is substantially better than the other by various threshold margins (τ):

```{r threshold-table}
kable(params$threshold_stats,
      format = "latex",
      booktabs = TRUE,
      caption = "Probability of exceeding threshold margins") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

## Summary Statistics

```{r intervals-table}
kable(params$intervals_tbl,
      format = "latex",
      booktabs = TRUE,
      caption = "Mean scores and 90% interval widths") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

## Methodology

Each decision aspect is modeled using Beta distributions parameterized from user-specified:
- **Importance:** Relative weight of this aspect (0 = low, 1 = high)
- **Uncertainty:** Confidence in the importance estimate (0 = very certain, 1 = very uncertain)
- **Presence (A & B):** Degree to which each choice exhibits this aspect
- **Uncertainty (A & B):** Confidence in presence estimates

The overall score for each choice is computed as:
$$\text{Score} = \sum_{i=1}^{n} \text{Importance}_i \times \text{Presence}_i$$

where the sum is taken over all included aspects. All probabilities and statistics are estimated from 5,000 Monte Carlo draws.

---

*Generated with Decision Space v3 using Claude Code*
